---
title: "GeoSociology Project Tables"
author: "Albert J. Bergesen and Kelsey E. Gonzalez"
date: "January 20, 2020"
header-includes:
   - \usepackage{dcolumn}
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(kableExtra) #printing normal tables 
library(stargazer) #printing regression tables 
library(rworldmap)
```

```{r}
df <- read_csv("data_output/countries_merged.csv") %>% drop_na() #drop NAs

```


# Descriptive Statistics
```{r}

df %>% 
  select(p_combwater, p_mount_tot, country, abortion2) %>% 
  mutate(abortion2 = ifelse(abortion2 == "Pro_Choice", 1, 0)) %>% 
  group_by(country) %>% 
  summarize(Water = first(p_combwater),
            Mountains = first(p_mount_tot),
            Neither = 1 - Water - Mountains,
            Neither = ifelse(Neither < 0, 0, Neither),
            abortion2 = mean(abortion2))  %>% 
  pivot_longer(-c(country, abortion2), names_to = "type", values_to = "percent") %>% 
  ggplot(aes(x = reorder(country, abortion2), y = percent, fill = type)) +
    geom_col()+
    theme(axis.text.x = element_text(size=8, angle=90, vjust=0.5, hjust=1)) +
    ggtitle("Figure 1: Border Distributions by Country sorted by liberality",
            subtitle = "Sorted from least accepting of abortion to most") +
    xlab("") + ylab("Percent of Border") + 
  scale_fill_manual(values=c("#397741", "#E69F00", "#56B4E9", "#FFFFFF"))

```

```{r}

countries <- df %>% 
  group_by(country) %>% 
  summarize(water = first(p_combwater),
            mountains = first(p_mount_tot)) 
         
# ten_countries <- countries %>% 
#   select(country) %>% 
#   sample_n(.,14) 
# ten_countries <- rbind(ten_countries, "Switzerland", "Denmark", "Hungary")
ten_countries <- c("Austria", "Bulgaria", "Romania", "Sweden", "Norway",
                   "Russia", "Estonia", "Latvia", "Ireland", "Switzerland",
                   "Denmark", "Hungary", "Slovak Republic", "Croatia")

      
countries <- countries %>% 
    mutate(label = ifelse(country %in% ten_countries, 
                        as.character(country), 
                        ""))

  ggplot(countries,
         aes(x = water, y = mountains)) +
    geom_point() +
    ggrepel::geom_text_repel(aes(label = label),
                  size = 4.5,
                  point.padding = .2,
                  box.padding = .3,
                  force = 1,
                  min.segment.length = 0)+
    ggtitle("Figure 2: Border Distributions by Country") +
    xlab("Percentage of Border that is Water") + 
    ylab("Percentage of Border that is Mountainous")
  
  
```

```{r, results='hide'}


malDF <- df %>% 
  mutate(abortion = ifelse(abortion2 == "Pro_Choice", 1, 0),
         gay_marriage = ifelse(gay_marriage2 == "Pro_Marriage_Equality", 1, 0),
         jews_neighbor = ifelse(jews_neighbor == "Accepts_Jews", 1, 0),
         muslims_neighbor = ifelse(muslims_neighbor == "Accepts_Muslims",1, 0)) %>% 
  group_by(country) %>% 
  summarize(abortion = mean(abortion),
            gay_marriage = mean(gay_marriage),
            jews_neighbor = mean(jews_neighbor),
            muslims_neighbor = mean(muslims_neighbor)) %>% 
  pivot_longer(-country, names_to = "variable", values_to = "percent") 

abortion <- malDF %>% 
  filter(variable == "abortion") %>% 
  rename(`Percent Pro-Life` = percent)

gay_marriage <- malDF %>% 
  filter(variable == "gay_marriage")  %>% 
  rename(`Percent Pro Marriage-Equality` = percent)

jews_neighbor <- malDF %>% 
  filter(variable == "jews_neighbor")  %>% 
  rename(`Percent Accepts Jewish Neighbors` = percent)

muslims_neighbor <- malDF %>% 
  filter(variable == "muslims_neighbor")  %>% 
  rename(`Percent Accepts Muslim Neighbors` = percent)

abortion <- joinCountryData2Map(abortion, joinCode = "NAME",
                              nameJoinColumn = "country")

gay_marriage <- joinCountryData2Map(gay_marriage, joinCode = "NAME",
                                nameJoinColumn = "country")

jews_neighbor <- joinCountryData2Map(jews_neighbor, joinCode = "NAME",
                                nameJoinColumn = "country")

muslims_neighbor <- joinCountryData2Map(muslims_neighbor, joinCode = "NAME",
                                nameJoinColumn = "country")
```

```{r}
## Specify the colourPalette argument
abortion <- mapCountryData(abortion, 
                      nameColumnToPlot="Percent Pro-Life", 
                      catMethod = "pretty",
                      missingCountryCol = gray(.8), 
                      xlim = c(-20, 59),
                      ylim = c(35, 71),
                      asp = 1) 
gay_marriage <- mapCountryData(gay_marriage, 
                           nameColumnToPlot="Percent Pro Marriage-Equality", 
                           catMethod = "pretty",
                           missingCountryCol = gray(.8), 
                           xlim = c(-20, 59),
                           ylim = c(35, 71),
                           asp = 1) 
jews_neighbor <- mapCountryData(jews_neighbor, 
                           nameColumnToPlot="Percent Accepts Jewish Neighbors", 
                           catMethod = "pretty",
                           missingCountryCol = gray(.8), 
                           xlim = c(-20, 59),
                           ylim = c(35, 71),
                           asp = 1) 
muslims_neighbor <- mapCountryData(muslims_neighbor, 
                           nameColumnToPlot="Percent Accepts Muslim Neighbors", 
                           catMethod = "pretty",
                           missingCountryCol = gray(.8), 
                           xlim = c(-20, 59),
                           ylim = c(35, 71),
                           asp = 1) 
```



```{r}
props <- df %>% 
  mutate(high = ifelse(country == "Switzerland", country, NA),
         high = ifelse(country == "Denmark", country, high),
         high = ifelse(country == "Hungary", country, high)) 


proportions_all <- as.data.frame(rbind(as.data.frame(prop.table(table(props$jews_neighbor))),
                                       as.data.frame(prop.table(table(props$muslims_neighbor))),
                                       as.data.frame(prop.table(table(props$religious))),
                                       as.data.frame(prop.table(table(props$gay_marriage2))),
                                       as.data.frame(prop.table(table(props$abortion2)))))

colnames(proportions_all) <- c("Variable","Overall")

proportions <- as.data.frame(rbind(prop.table(table(props$jews_neighbor,props$high), 2),
                                   prop.table(table(props$muslims_neighbor,props$high), 2),
                                   prop.table(table(props$religious,props$high), 2),
                                   prop.table(table(props$gay_marriage2,props$high), 2),
                                   prop.table(table(props$abortion2,props$high), 2)))
  
total_proportions_table <- cbind(proportions_all,proportions)
```




```{r eval=FALSE}
total_proportions_table %>% 
  select(-Variable) %>% 
  kable("latex", round(digits = 3)) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("", 
                     "All Countries" = 1, 
                     "High Water" = 1, 
                     "Low Water, \n Low Mountains" = 1, 
                     "High Mountains" = 1)) %>% 
  add_header_above(c("", 
                     "All Countries" = 1, 
                     "Example Countries" = 3))

```
\begin{table}[H]
\centering
\caption{Attitudinal Responses Over Total Group and Selected Countries}
\begin{tabular}{l|r|r|r|r}
\hline
\multicolumn{1}{c|}{} & \multicolumn{1}{c|}{All Countries} & \multicolumn{3}{c}{Example Countries} \\
\cline{2-2} \cline{3-5}
\multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{High Water} & \multicolumn{1}{c|}{\makecell[c]{Low Water, \\ Low Mountains}} & \multicolumn{1}{c}{High Mountains} \\
\cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
  & Overall & Denmark & Hungary & Switzerland\\
\hline
Accepts Jews as Neighbors & 0.872 & 0.984 & 0.829 & 0.927\\
Wouldn't Accept Jews as Neighbors & 0.128 & 0.016 & 0.171 & 0.073\\
\hline
Accepts Muslims as Neighbors & 0.731 & 0.927 & 0.421 & 0.868\\
Wouldn't Muslims Jews as Neighbors & 0.269 & 0.073 & 0.579 & 0.132\\
\hline
Not Religious & 0.476 & 0.483 & 0.610 & 0.543\\
Religious & 0.524 & 0.517 & 0.390 & 0.457\\
\hline
Against Marriage Equality & 0.538 & 0.089 & 0.700 & 0.177\\
Pro Marriage Equality & 0.462 & 0.911 & 0.300 & 0.823\\
\hline
Pro Choice (Abortion) & 0.669 & 0.948 & 0.739 & 0.820\\
Pro Life (Abortion) & 0.331 & 0.052 & 0.261 & 0.180\\
\hline
\hline
N & \multicolumn{4}{l}{44,708}                   \\
\end{tabular}
\end{table}



```{r eval=FALSE}
df %>% 
  group_by(country) %>% 
  summarize(`Internet Users` = mean(interusers),
            `Percent \n Urban Residents` = 0.01*mean(perc_urban),
            `Percent Entrolled \n in Tertiary Educ` = 0.01*mean(tert),
            `GDP Per Capita` = mean(GDP),
            N = n()) %>% 
  kable("latex", 
        round(digits = 2),
        escape = FALSE,
        col.names = c("Country",
                      "Internet Users",
                      "Urban Residents",
                      "Enrolled in Tertiary Educ",
                      "GDP Per Capita",
                      "N")) %>% 
  kable_styling(position = "center") 
```
\begin{table}[H]
\centering
\caption{Country-Level Variables by Country}

\begin{tabular}{l|r|r|r|r|r}
\hline
Country & Internet Users & \% Urban Residents &  \makecell{\% Enrolled in \\ Tertiary Educ} & GDP Per Capita & Count \\
\hline
Armenia & 0.70 & 0.63 & 0.52 & 12433.09 & 1348\\
\hline
Austria & 0.88 & 0.58 & 0.86 & 455736.58 & 1548\\
\hline
Belarus & 0.74 & 0.79 & 0.87 & 59662.50 & 927\\
\hline
Belgium & 0.88 & 0.98 & 0.76 & 531766.94 & 1299\\
\hline
Bosnia & 0.69 & 0.48 & 0.23 & 19781.78 & 672\\
\hline
Bulgaria & 0.63 & 0.75 & 0.71 & 65132.95 & 1214\\
\hline
Croatia & 0.67 & 0.57 & 0.67 & 60805.66 & 1388\\
\hline
Czech Republic & 0.79 & 0.74 & 0.64 & 244105.22 & 1189\\
\hline
Denmark & 0.97 & 0.88 & 0.81 & 351299.59 & 1360\\
\hline
Estonia & 0.88 & 0.69 & 0.71 & 30284.89 & 1283\\
\hline
Finland & 0.87 & 0.85 & 0.87 & 275683.14 & 1243\\
\hline
France & 0.81 & 0.80 & 0.64 & 2777535.24 & 1541\\
\hline
Georgia & 0.60 & 0.59 & 0.58 & 16209.82 & 1196\\
\hline
Germany & 0.84 & 0.77 & 0.68 & 3996759.29 & 1898\\
\hline
Greece & 0.70 & 0.79 & 1.26 & 218031.84 & 1241\\
\hline
Hungary & 0.77 & 0.71 & 0.48 & 155703.07 & 987\\
\hline
Ireland & 0.85 & 0.63 & 0.78 & 375902.68 & 1239\\
\hline
Italy & 0.61 & 0.70 & 0.63 & 2073901.99 & 1518\\
\hline
Kazakhstan & 0.76 & 0.57 & 0.53 & 170538.87 & 476\\
\hline
Latvia & 0.81 & 0.68 & 0.88 & 34849.08 & 1116\\
\hline
Lithuania & 0.78 & 0.68 & 0.71 & 53251.37 & 1232\\
\hline
Moldova & 0.76 & 0.43 & 0.41 & 11309.08 & 1568\\
\hline
Netherlands & 0.93 & 0.91 & 0.80 & 912872.33 & 1349\\
\hline
Norway & 0.97 & 0.82 & 0.82 & 434750.94 & 1259\\
\hline
Poland & 0.76 & 0.60 & 0.67 & 585782.87 & 1097\\
\hline
Portugal & 0.74 & 0.65 & 0.63 & 237978.94 & 1209\\
\hline
Romania & 0.64 & 0.54 & 0.48 & 239552.52 & 1202\\
\hline
Russia & 0.76 & 0.74 & 0.82 & 1657553.77 & 1336\\
\hline
Serbia & 0.70 & 0.56 & 0.66 & 50508.37 & 1342\\
\hline
Slovak Republic & 0.82 & 0.54 & 0.48 & 106472.19 & 1188\\
\hline
Spain & 0.85 & 0.80 & 0.91 & 1426189.14 & 1215\\
\hline
Sweden & 0.96 & 0.87 & 0.64 & 551031.68 & 1337\\
\hline
Switzerland & 0.94 & 0.74 & 0.58 & 705501.30 & 1419\\
\hline
Ukraine & 0.57 & 0.69 & 0.83 & 130832.37 & 1607\\
\hline
United Kingdom & 0.95 & 0.83 & 0.59 & 2825207.95 & 1665\\
\hline
\end{tabular}
\end{table}









\pagebreak
 
# Logistic Regression Results
```{r, results = "hide"}
reg <- df %>% 
  mutate(`Pro Abortion` = relevel(as.factor(abortion2), 
                                  ref = "Pro_Life"),
         
         `Marriage Equality` = relevel(as.factor(gay_marriage2), 
                                       ref = "Against_Marriage_Equality"),
         
         `Ok with Jewish Neighbor` = relevel(as.factor(jews_neighbor),
                                             ref = "Rejects_Jews"),

         `Ok with Muslim Neighbor` = relevel(as.factor(muslims_neighbor),
                                             ref = "Rejects_Muslims"),
         
         `Respondent is Religious` = relevel(as.factor(religious),
                                             ref = "Not_Religious")) %>% 
  rename(`Water Border` = p_combwater,
         `Mountainous Border` = p_mount_tot,
         `Percentage Internet Users` = interusers,
         `Percentage Urban Residents` = perc_urban,
         `Logged GDP` = l_GDP,
         `Percentage Tertiary Educ`= tert)

model1  <- glm(`Pro Abortion` ~ `Water Border` + 
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
model2  <- glm(`Marriage Equality` ~ `Water Border` + 
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
model3  <- glm(`Ok with Jewish Neighbor` ~ `Water Border` + 
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
model4  <- glm(`Ok with Muslim Neighbor` ~ `Water Border` + 
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))

# stargazer(model1, model2, model3, model4, 
          # title="Regression Results", align=TRUE)

write.csv(reg, file = "reg_for_modeling.csv")
```

\begin{table}[H] 
\centering 
\caption{Full Regression Results of Four Dependent Variables} 
\label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & 
\multicolumn{1}{c}{Pro Abortion} & 
\multicolumn{1}{c}{\makecell[c]{Marriage Equality}} & 
\multicolumn{1}{c}{\makecell[c]{Ok with \\ Jewish Neighbor}} & 
\multicolumn{1}{c}{\makecell[c]{Ok with \\ Muslim Neighbor}} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 

 &  &  &  &  \\ 
\textit{Independent Variables} &  &  &  &  \\ 
\hline
 Water Border & 1.449^{***} & 1.951^{***} & 3.122 ^{***} & 4.434^{***} \\ 
  & (0.049) & (0.048) & (0.068) & (0.051) \\ 
  & & & & \\ 
 Mountainous Border & 2.463^{***} & 2.905 ^{***} & 5.585^{***} & 11.675^{***} \\ 
  & (0.062) & (0.068) & (0.088) & (0.068) \\ 
  & & & & \\ 
  
 &  &  &  &  \\ 
\textit{Country-Level Controls} &  &  &  &  \\ 
\hline

 Percentage Internet Users & 29.114^{***} & 325.856^{***} & 22.494^{***} & 4.054^{***} \\ 
  & (0.118) & (0.131) & (0.161) & (0.130) \\ 
  & & & & \\ 
 Percentage Urban Residents & 1.044^{***} & 1.022^{***} & 1.027^{***} & 1.013^{***} \\ 
  & (0.001) & (0.002) & (0.002) & (0.001) \\ 
  & & & & \\ 
 Percentage Tertiary Educ & 0.986^{***} & 0.991^{***} & 0.990^{***} & 0.993^{***} \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  & & & & \\ 
 Logged GDP` & 1.080^{***} & 1.613^{***} & 0.946^{***} & 1.122^{***} \\ 
  & (0.010) & (0.011) & (0.013) & (0.010) \\ 
  & & & & \\ 

 &  &  &  &  \\ 
\textit{Individual-Level Controls} &  &  &  &  \\ 
\hline 

 Respondent is Religious & 0.529^{***} & 0.581^{***} & 1.081^{***} & 1.030^{***} \\ 
  & (0.023) & (0.024) & (0.031) & (0.024) \\ 
  & & & & \\ 
 Constant & 0.010^{***} & 0.00001^{***} & 0.210^{***} & 0.063^{***} \\ 
  & (0.116) & (0.135) & (0.156) & (0.122) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & \multicolumn{1}{c}{44,708} & \multicolumn{1}{c}{44,708} & \multicolumn{1}{c}{44,708} & \multicolumn{1}{c}{44,708} \\ 

Log Likelihood & \multicolumn{1}{c}{-23,889.130} & \multicolumn{1}{c}{-21,853.460} & \multicolumn{1}{c}{-15,727.390} & \multicolumn{1}{c}{-22,935.600} \\ 

Akaike Inf. Crit. & \multicolumn{1}{c}{47,794.250} & \multicolumn{1}{c}{43,722.920} & \multicolumn{1}{c}{31,470.780} & \multicolumn{1}{c}{45,887.190} \\ 

\hline 
\hline \\[-1.8ex] 
\multicolumn{2}{l}{\makecell[c]{Note: Standard Errors In Parentheses; \\ Coeffients as Odds-Ratios}}  &
\multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 





\pagebreak

# Appendix


```{r , results='hide'}
model1a  <- glm(`Pro Abortion` ~ `Water Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
model1b  <- glm(`Pro Abortion` ~  
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
```

```{r results='asis'}
stargazer(model1a, model1b, model1,
          title="Regression Results for Abortion Attitudes",
          align=TRUE,
          apply.coef = exp,
          notes = "Standard Errors In Parentheses; \\ Coeffients as Odds-Ratios",
          notes.append = TRUE)
```



```{r}
model2a  <- glm(`Marriage Equality` ~ `Water Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
model2b  <- glm(`Marriage Equality` ~ 
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
```

```{r results='asis'}
stargazer(model2a, model2b, model2,
          title="Regression Results for Marriage Equality Attitudes", 
          align=TRUE,
          apply.coef = exp,
          notes = "Standard Errors In Parentheses; \\ Coeffients as Odds-Ratios",
          notes.append = TRUE)
```

```{r}
model3a  <- glm(`Ok with Jewish Neighbor` ~ `Water Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
model3b  <- glm(`Ok with Jewish Neighbor` ~ 
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
```

```{r results='asis'}

stargazer(model3a, model3b, model3,
          title="Regression Results for Jewish Neighbor Acceptance  Attitudes", 
          align=TRUE,
          apply.coef = exp,
          notes = "Standard Errors In Parentheses; \\ Coeffients as Odds-Ratios",
          notes.append = TRUE)                
```                
                
```{r}                
model4a  <- glm(`Ok with Muslim Neighbor` ~ `Water Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
model4b  <- glm(`Ok with Muslim Neighbor` ~ 
                  `Mountainous Border` + 
                  `Percentage Internet Users` + 
                  `Percentage Urban Residents` + 
                  `Percentage Tertiary Educ` + 
                  `Logged GDP` + 
                  `Respondent is Religious`,
                data = reg, 
                family = "binomial"(link="logit"))
```

```{r results='asis'}
stargazer(model4a, model4b, model4,
          title="Regression Results for Muslim Neighbor Acceptance Attitudes", 
          align=TRUE,
          apply.coef = exp,
          notes = "Standard Errors In Parentheses; \\ Coeffients as Odds-Ratios",
          notes.append = TRUE)    
```
