---
title: "GeoSociology Data Wrangling"
author: "Kelsey E. Gonzalez"
date: "January 15, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(skimr)
library(forcats)

borders <- read_csv("data_orig/borders.csv")
eastern <- read_csv("data_orig/eastern.csv")
western <- read_csv("data_orig/western.csv")
```

fix Italy's weird border number (adding up to a little over one)
```{r}
borders <- borders %>% 
  mutate(p_mount_land = ifelse(country == "Italy", 1, p_mount_land),
         p_mount_tot = ifelse(country == "Italy", (1-p_combwater), p_mount_tot),)
```


clean eastern dataframe by renaming columns and merging muslim and non-muslim religiosity into new variable, religious
```{r}
eastern <- 
  eastern %>% 
  rename(jews_neighbor = Q59b,
         muslims_neighbor  = Q60b,
         catholics_neighbor = Q61b,
         orthodox_neighbor = Q62B,
         id = CASEID,
         gay_marriage = Q10,
         abortion = Q11,
         country = COUNTRY,
         religious_c = Q41,
         religious_m = Q37) %>% 
    mutate(religious_c2 = as.factor(religious_c),
         religious_m2 = as.factor(religious_m),
         religious_c2 = fct_recode(religious_c2, 
                                   Religious = "A few times a year",       
                                   Religious = "More than once a week",   
                                   Religious = "Once a week",              
                                   Religious = "Once or twice a month",   
                                   Not_Religious = "Seldom",
                                   Not_Religious = "Never",                    
                                   na = "Don't know (DO NOT READ)", 
                                   na = "Refused (DO NOT READ)"),
         religious_m2 = fct_recode(religious_m2, 
                                   Religious = "A few times a year especially for Eid",       
                                   Religious = "More than once a week",   
                                   Religious = "Once a week for Friday Prayer",              
                                   Religious = "Once or twice a month",   
                                   Not_Religious = "Seldom",
                                   Not_Religious = "Never",                    
                                   na = "Don't know (DO NOT READ)", 
                                   na = "Refused (DO NOT READ)"),
         religious_c2 = as.character(religious_c2),
         religious_m2 = as.character(religious_m2)) %>% 
    mutate(religious = ifelse(is.na(religious_c2), religious_m2, religious_c2)) %>% 
    mutate(religious = ifelse(religious == "na",NA, religious)) %>%
    select(-c(religious_c2, religious_c, religious_m, religious_m2))
```

clean western dataframe by renaming columns and merging muslim and non-muslim religiosity into new variable, religious
```{r}
western <-
  western %>% 
  rename(jews_neighbor = Q36b,
         muslims_neighbor  = Q37b,
         catholics_neighbor = Q38b,
         protestants_neighbor = Q39b,
         id = QRID,
         gay_marriage = Q5,
         abortion = Q6,
         religious_c = Q15a,
         religious_m = Q15b) %>% 
  mutate(religious_c2 = as.factor(religious_c),
         religious_m2 = as.factor(religious_m),
         religious_c2 = fct_recode(religious_c2, 
                                   Religious = "A few times a year",       
                                   Religious = "More than once a week",   
                                   Religious = "Once a week",              
                                   Religious = "Once or twice a month",   
                                   Not_Religious = "Seldom",
                                   Not_Religious = "Never",                    
                                   na = "Don't know (DO NOT READ)", 
                                   na = "Refused (DO NOT READ)"),
         religious_m2 = fct_recode(religious_m2, 
                                   Religious = "A few times a year especially for Eid",       
                                   Religious = "More than once a week",   
                                   Religious = "Once a week for Friday Prayer",              
                                   Religious = "Once or twice a month",   
                                   Not_Religious = "Seldom",
                                   Not_Religious = "Never",                    
                                   na = "Don't know (DO NOT READ)", 
                                   na = "Refused (DO NOT READ)"),
         religious_c2 = as.character(religious_c2),
         religious_m2 = as.character(religious_m2)) %>% 
    mutate(religious = ifelse(is.na(religious_c2), religious_m2, religious_c2)) %>% 
    mutate(religious = ifelse(religious == "na",NA, religious)) %>%
    select(-c(religious_c2, religious_c, religious_m, religious_m2))
```

append western to eastern in new dataframe, europe. Remove orthodox and protestant columns as they're not consistent across the datasets. 
```{r}
europe <- bind_rows(eastern, western) %>% select(-c(orthodox_neighbor, protestants_neighbor))
```

rename some of the border's country labels to match with the europe df variables, including russia and bosnia.
```{r}
borders <- 
  borders %>% 
  mutate(country = as.factor(country),
         country = fct_recode(country, 
                              Russia = "Russian Federation",
                              Bosnia = "Bosnia and Herzegovina"),
         country = as.character(country)) %>% 
  select(country, 
         p_combwater,
         p_mount_tot,
         p_mount_land,
         interusers,
         perc_urban,
         GDP,
         l_GDP,
         tert)
```

merge europe with borders
```{r}
countries_merged <- europe %>% 
  left_join(borders, by = "country") 
```

a little more wrangling to clean NAs and collapse variables
```{r}
countries_merged <-
  countries_merged %>% 
    mutate(jews_neighbor = as.factor(jews_neighbor),
           jews_neighbor = fct_recode(jews_neighbor,
                                NULL = "Depends (VOL.)",
                                NULL = "Don't know (DO NOT READ)",
                                NULL = "Other / Both / Neither / Depends (DO NOT READ)",
                                NULL = "Refused (DO NOT READ)",
                                Accepts_Jews = "Yes",
                                Rejects_Jews = "No")) %>% 
    mutate(muslims_neighbor = as.factor(muslims_neighbor),
           muslims_neighbor = fct_recode(muslims_neighbor,
                                NULL = "Depends (VOL.)",
                                NULL = "Don't know (DO NOT READ)",
                                NULL = "Other / Both / Neither / Depends (DO NOT READ)",
                                NULL = "Refused (DO NOT READ)",
                                Accepts_Muslims= "Yes",
                                Rejects_Muslims= "No")) %>% 
    mutate(gay_marriage = as.factor(gay_marriage),
           gay_marriage2 = fct_recode(gay_marriage,
                                NULL = "Don't know (DO NOT READ)",
                                NULL = "Refused (DO NOT READ)",
                                Pro_Marriage_Equality = "Strongly favor",
                                Pro_Marriage_Equality = "Favor",
                                Against_Marriage_Equality = "Strongly oppose",
                                Against_Marriage_Equality = "Oppose",)) %>%
    mutate(abortion = as.factor(abortion),
           abortion2 = fct_recode(abortion,
                                NULL = "Don't know (DO NOT READ)",
                                NULL = "Refused (DO NOT READ)",
                                Pro_Choice = "Legal in all cases",
                                Pro_Choice = "Legal in most cases",
                                Pro_Life = "Illegal in all cases",
                                Pro_Life = "Illegal in most cases"),
           country = as.factor(country)) %>% 
  select(-c(abortion, gay_marriage, catholics_neighbor))
write_csv(countries_merged, path = "data_output/countries_merged.csv")  
```


